Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-16 content/contribution/continuous-datalog.tex
minor modifications to cite IStream/DStream, and explain "entailment precedes negation" in terms of justification from windows over S

@@

			Facts may only be negated after they have been entailed.

>>>>

			Streams $P$ and $N$ are therefore the continuous reasoning equivalents of the streams produced by the \emph{IStream} and \emph{DStream} operators of the \emph{CQL} continuous query language \citep{CQL} respectively.

@@

			Facts may only be negated by some part of their justification leaving the sliding window $W^{S,R}_{i}$, this necessarily being after they were entailed.
